Viewing Computer Science through Citation Analysis

### 2020-05-11 Scientometrics/rebuttal2/rebuttal_letter_2.tex

\noindent George Chacko, PhD

\newpage

\section*{Reviewer 1} 1. By visibility of the images Reviewer means that Fig. 3 (especially a \& b) labels on x and y axis are of very small font. 2. After the revision, paper is better understandable then before. Also, Since authors have 
used DBLP and Scopus, Reviewer would like authors to add  some discussion in the introduction about other two widely used bibliometric sources i.e google scholar and web of science and mention pros and cons of why they have used 
the said two and why not these two. Authors may take hint of such discussion from papers like: Zavadskas, E. K., Skibniewski, M. J., \& Antucheviciene, J. (2014). Performance analysis of Civil Engineering Journals based on the Web of Science® 
database. Archives of Civil and Mechanical Engineering, 14(4), 519-527. Shukla, A. K., Janmaijaya, M., Abraham, A., \& Muhuri, P. K. (2019). Engineering applications of artificial intelligence: A bibliometric analysis of 30 years (1988-2018). 
Engineering Applications of Artificial Intelligence, 85, 517-532.ienc

\subsection*{Response}
\begin{enumerate}
\item Fig 3 has been revised to increase the size of x-axis and y-axis labels and scaled by placing it in landscape mode. Thank you for clarifying our question.
\item We have carefully considered the suggestion, which we appreciate, to expand the introduction to discuss Google Scholar and Web of Science as alternatives to Scopus. 
However, we believe that an expanded discussion of the perceived relative merits of these commercial databases is distracting since the reasons advanced in the literature to recommend one 
over the other are contextual, disciplinary, and often subjective. We have added a sentence, however, mentioning Scopus and Web of Science and citing Archambault 2009 (below).

@@

Our use of DBLP is justified in the Introduction as a `reference bibliography for computer science'. We also mention the limitations of ASJC and other journal based classifications to identify 
disciplines, hence our reliance on article level clusters. In the course of responding to this point. we found a conference paper by Pham and Klamma, that also identifies DBLP as important 
to the field of computer science, and we have included it in our bibliography.

In terms of Scopus, the choice was simple. Our implementation of Scopus is full-featured (all ~90 million records and associated metadata are resident on our servers). Thus, we do not need to scrape 
data or use a throttled API to access information. We also chose Scopus over Web of Science because of its its well designed XML structure. We previously used Web of Science (also as resident on 
our servers) and our experience is that the two are comprehensive in terms of coverage but clearly not identical. This is consistent with Archambault's observations. Lastly, our budget does not permit us to afford two subscriptions.

@@

Google Scholar is a non-starter as far as we are concerned. It suffers from false positives, duplicates, includes grey literature, and does not allow large scale analysis. As mentioned by Martin-Martin et al. (2019),
`Google Scholar, Web of Science, and Scopus: Which is best for me?' on the London School of Economics website, \emph{``The question, as our colleague Professor Harzing put it, is whether 
we are ready to accept a trade-off: going beyond the comfortable and orderly borders of curated databases in exchange for more diverse coverage.''} We do not consider this trade-off useful for 
our purposes. Accordingly, we find value in the orderly borders of the Scopus and DBLP curated databases over the use of Google Scholar for this study.

We examined the references suggested by the reviewer; Zavadskas et al. (2014) and Shukla et al. (2019). The text within is not inconsistent with the points we make in our first paragraph but did not 
provide additional insight that would persuade us to expand the Introduction further. For example, Shukla et al. state that.``WoS is the first multidisciplinary bibliographic index of journal publications designed. 
It is considered a standard data source for bibliometrics. Other databases such as Scopus by Elsevier are also used by bibliometricians." and ``A comparison with other indexing platforms such as Scopus, 
Google Scholar can be a good future scope of this study.''

To examine the issue raised by the reviewer, we read some comprehensive comparisons of these databases (below) but did not find compelling reasons to further expand the Introduction. Archambault's 
paper is relevant (or at least consistent with) our comment that the choice of either Web of Science or Scopus is contextual and can be subjective. 
MacRoberts and MacRoberts assert that all bibliographic databases have limitations and we agree.

@@

This manuscript overviews the fields of computer science by the means of clustering for networks of direct citation or co-citation. Comparing with the previous version, the manuscript 
becomes easy for readers to understand the content along the purpose. However, there are some mis-spelligs or mis-formattings.
- Please search "co-citation. .", and delete one of these periods.
- Please search "by takimg advantage of modern bibliographic resources", and change "takimg" to "taking".
- Please search "discuss our findings, Overall", and change from comma to period.
- Please search "y:axis", and change to "y-axis".

The formats of second-level headings are mixed like "Co-Citation." and "Scopus data", whose difference is to finish with a period or without it. Please unify the format, and the reviewer recommends 
the italic (and bold) "Co-Citation:", refering to\\ http://journals.ieeeauthorcenter.ieee.org/wp-content/uploads/sites/7/IEEE-Editorial-Style-Manual.pdf.
- "DBLP dataA" must be "DBLP data A".
- I guess that "Merging and graph construction" is also one of the second-level headings.
I have judged that these are proofreading tasks, but the number of these is large. Thus, please check your manuscript to repair careless mistakes by yourself. I expect I cannot find all.
As a result, I recommend minor revision close to proofreading-level. About the content, there is no problem

\subsection*{Response}

We thank the reviewer for these comments. We have corrected all the typographic errors noted and made further corrections at the proofreading level to try and ensure consistency. Some of these errors 
seem to have been generated by the \emph{changes} package juxtaposing sections of text when run in clean mode. We have constructed a clean copy.

### 2020-05-11 Scientometrics/rebuttal2/comp_revised_2.tex
R2

The purpose of this study is to develop an improved understanding of the structure of the field of computer science relative to the landmark study of Salton and Bergmark forty years ago. We extend their work by taking advantage of modern bibliographic resources and clustering technologies and using a combination of article and journal approaches to study trends in the computer science literature. We also consider connections to other fields, especially biology, since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences. As a source of computer  literature, we use DBLP, a reference bibliography for computer science~\cite{dblp_ref,pham_2010}. The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research. We construct clusters of articles using either direct citation or co-citations and match these clusters to ASJC categories to place them in context. We also aligned clusters from direct citations to those from co-citations and discuss our findings. Overall, we note cross category clusters with different degrees of interaction with fields outside computer science.

\section{Materials and Methods}
\label{sec:methods}

\emph{Overview} Our underlying assumption is that, notwithstanding incomplete coverage, records in DBLP are greatly enriched for computer science~\cite{dblp_ref,pham_2010}. Therefore, the contents of DBLP are an excellent sample of the computer science literature to analyze. The workflow described in the following paragraphs of Materials and Methods, consists at a high-level of (i) merging the DBLP and Scopus datasets using digital object identifiers(DOIs) (ii) extracting cited references for the articles common to DBLP and Scopus (iii) clustering by direct citation and by our modification of co-citation based clustering. The outcome was a dataset of 8,000,411 publications.

@@

\emph {Direct Citation.} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, and that has previously been applied to citation data~\cite{subelj_clustering_2016}. We used v1.2 in our experiments. The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus, which requires the number of clusters to be formed as an input parameter. In preliminary experiments, we varied the number of clusters to be formed between 10 and 50 clusters (data not shown).  At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one,
so that 20 clusters is a good choice with respect to the criteria specified in~\cite{subelj_clustering_2016}. Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}), analogous to Level 1 of Waltman and van Eck's mapping of nearly 10 million publications but focused on the DBLP bibliography rather than a broader Web of Science sample~\cite{waltman_new_2012}.

@@

\emph{Co-Citation.} For an alternate view of these DBLP data, we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles \cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}. Co-citation, first described independently by Small and Marshakova in 1973 \cite{marshakova-shaikevich_co-citation_1973}, provides insight into the emergence of new ideas derived from the association of previously independent ones. Unlike clustering by direct citation, where every input publication is assigned to a cluster and every citation is weighted equally, the co-citation relationship between papers is weighted to represent the strength of the co-citation history. Because this produces a weighted graph, clustering methods that address weights are required. Clustering by co-citation also considers weak inter-cluster interactions that involve modifications to standard clustering approaches. \cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.

@@

We began by identifying highly cited articles in \emph{comp} and selected those in the 90th percentile (212,311 articles). We then identified ~4.3 million publications in Scopus that cite these 212,311 articles. For each of the 4.3 million citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication. The cited reference pairs generated were then restricted to those where both members of a pair were in the set of 212,311 highly cited papers previously identified. A total of 46,463,117 unique co-cited pairs were thus obtained. The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979} to limit dominance by areas with high citation activity. These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency. \par

@@

\section{Results}
\label{sec:results}

@@

To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other (Fig.~\ref{fig:graclus_cocit_fig}).
 At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters. This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and,  by extension, tend towards disciplinarity rather than interdisciplinarity.

\section{Discussion} 
Considering expansion and diversification of the field of computer science, we revisited its characterization by Salton and Bergmark in 1979~\cite{salton_citation_1979}. In comparison to \cite{salton_citation_1979}, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  approximately 7 million and 88 million publications respectively. By linking the two datasets, we were able to harvest citation data as well as other metadata that enabled theo construct article level clusters in two different ways and reconciliation with the Scopus ASJC classification, for a journal level perspective.

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
\includegraphics[scale=0.6]{graclus_comparison.pdf}
% generated by conductance.R script
% figure caption is below the figure
\caption{Conductance Measurements of Clusters Generated by Graclus of the direct citation dataset.  2,685,356 DBLP publications, 7,129,006 cited references, and 44,296,381 citations were clustered using Graclus into 18 (grac\_18), 20 (grac\_20), or 22 (grac-22) clusters. Conductance, $\phi(S)$, was measured for these clusters considering only the edges between publications using the formula: $\phi(S)=|\partial(S)|/min(vol(S),2m-vol(S)$, where $\partial(S)$ is the boundary (number of edges leaving a set), vol(S) is volume of a set of vertices as the sum of the degrees of the vertices in a set, and $m$ is the number of undirected edges in a set~\cite{shun_parallel_2016}.}
\label{fig:graclus_comparison_conductance}       
\end{figure}

@@

\begin{table}[ht]
\caption{Descriptive statistics of the 20 clusters produced from the \emph{dataset} using Graclus (direct citation).  The number of publications in each cluster, the conductance~\cite{shun_parallel_2016} of each cluster, the total number ASJC minor subject area labels assigned to publications in each cluster and the number of 
unique labels in each cluster are shown.}
\label{tab:graclus}       
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
\noalign{\smallskip}\hline\noalign{\smallskip}
0 & 111,294 & 0.12 & 265,664 & 142 \\ 
1 & 117,057 & 0.14 & 246,960 & 166 \\ 
2 & 116,251 & 0.11 & 280,602 & 165 \\ 
3 & 353,366 & 0.15 & 881,693 & 200 \\ 
4 & 145,081 & 0.09 & 349,020 & 154 \\ 
5 & 92,097 & 0.17 & 248,168 & 186 \\ 
6 & 71,865 & 0.15 & 199,681 & 163 \\ 
7 & 179,927 & 0.18 & 465,181 & 202 \\ 
8 & 302,656 & 0.18 & 760,117 & 214 \\ 
9 & 69,520 & 0.19 & 197,031 & 174 \\ 
10 & 42,462 & 0.10 & 102,838 & 141 \\ 
11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
12 & 70,738 & 0.21 & 216,546 & 179 \\ 
13 & 105,232 & 0.17 & 289,318 & 187 \\ 
14 & 199,176 & 0.15 & 551,657 & 208 \\ 
15 & 64,384 & 0.17 & 195,679 & 167 \\ 
16 & 89,340 & 0.11 & 240,157 & 158 \\ 
17 & 50,817 & 0.14 & 181,531 & 179 \\ 
18 & 43,113 & 0.20 & 108,518 & 177 \\ 
19 & 12,615 & 0.80 & 36,583 & 229 \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Nucleating Co-citations.} For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label.}
\label{tab:centroid}       
\begin{tabular}{p{8 mm}p{42 mm}ll}
\hline\noalign{\smallskip}
Cluster & Nucleating Pair & NCF & Label \\
\noalign{\smallskip}\hline
18670 & 10.1016/j.cam.2015.03.057 10.1016/j.sigpro.2015.10.009 & 0.92 & Dynamical Systems \\
18892 & 10.1287/msom.1080.0228 10.1287/msom.1060.0190 & 0.72 & Operations Research\\ 
18918 & 10.1007/s11128-010-0177-y 10.1007/s11128-013-0567-z & 0.83 & Image Processing\\ 
18947 & 10.1109/TASE.2011.2160452 10.1109/TASE.2011.2178023 & 0.77 & Robotics\\ 
18956 & 10.1109/ICCV.2017.32 10.1109/ICCV.2017.31 & 0.84 & Computer Vision\\ 
18972 & 10.1109/ASE.2013.6693094 10.1145/2568225.2568254 & 0.69 & Software \\ 
18974 & 10.1016/j.amc.2009.03.023 10.1016/j.amc.2010.07.064 & 0.54 & Applied Mathematics\\ 
18983 & 10.1137/110848864 10.1137/110848876 & 0.66 & Optimization\\ 
18997 & 10.1504/IJMIC.2014.065339 10.1504/IJMIC.2015.068871 & 0.91 & Chaotic Systems \\ 
19008 & 10.1016/j.chb.2008.12.013 10.1016/j.chb.2008.12.012 & 0.63 & Hum Comp Interaction\\ 
19009 & 10.1109/AVSS.2017.8078491 10.1109/ICCV.2017.206 & 0.78 & Artificial Intelligence\\ 
19013 & 10.1145/2508859.2516668 10.1007/978-3-642-42045-0\_15 & 0.88 & Security\\ 
19026 & 10.1145/2541940.2541942 10.1109/HPCA.2014.6835965 & 0.81 & Architecture\\ 
19027 & 10.1016/S0305-0548(03)00250-8 10.1016/j.ejor.2006.03.013 & 0.82 & Graph algorithms\\ 
19030 & 10.1109/ICDE.2008.4497474 10.14778/1687627.1687666 & 0.69 & Databases \\ 
19031 & 10.1109/TMM.2005.843347 10.1109/TCE.2005.1405724 & 0.55 & Networks\\ 
19033 & 10.1109/TIFS.2014.2327757 10.1109/TCYB.2014.2376934 & 0.78 & Facial Recognition\\ 
19034 & 10.1016/j.neuroimage.2013.05.018 10.1016/j.neuroimage.2014.06.016 & 0.63 & Neurology\\ 
19035 & 10.1002/int.21933 10.1002/int.21927 & 1.09 & Intelligent Systems\\ 
19036 & 10.1006/jsco.2000.0402 10.1006/jsco.2000.0403 & 0.73 & Comp Geometry\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Nucleating Co-citations} Manually assigned labels for nucleating co-cited pairs (Table~\ref{tab:centroid}) are matched to the ASJC minor subject area that constitutes the largest fraction (shown as percentage in parentheses) of all nodes in the cluster. In cases of ties, both minor subject areas are shown. Abbreviations: Electrical and Electronic Engineering (EEE); Control and Systems Engineering (CSE).}
\label{tab:centroid_reconcile}       
\begin{tabular}{p{8 mm}p{42 mm}l}
\hline\noalign{\smallskip}
Cluster & Label & Minor Subject Area \\
\noalign{\smallskip}\hline
18670 & Dynamical Systems & (i) EEE (14) (ii) CSE (14) \\
18892 & Operations Research & EEE (24) \\ 
18918 & Image Processing & (i) EEE (17) (ii) Software (17) \\ 
18947 & Robotics & Software (12) \\ 
18956 & Computer Vision & Computer Graphics and Computer-Aided Design (21)\\ 
18972 & Software & Software (55) \\ 
18974 & Applied Mathematics & Applied Mathematics (12)\\ 
18983 & Optimization & EEE (35) \\ 
18997 & Chaotic Systems & CSE (23)\\ 
19008 & Hum Comp Interaction & Education (19)\\ 
19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
19013 & Security & Computer Science(all) (29)\\ 
19026 & Architecture & EEE (35) \\ 
19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
19030 & Databases & Software (19)\\ 
19031 & Networks & EEE (32)\\ 
19033 & Facial Recognition & Computer Vision and Pattern Recognition (18)\\ 
19034 & Neurology & Neurology (12)\\ 
19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
19036 & Comp Geometry & Software (10)\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

>>>>

The purpose of this study is to develop an improved understanding of the structure of the field of computer science relative to the landmark study of Salton and Bergmark forty years ago. We extend their work by taking advantage of modern bibliographic resources and clustering technologies and using a combination of article and journal approaches to study trends in the computer science literature. We also consider connections to other fields, especially biology, since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences. As a source of computer  literature, we use DBLP, a reference bibliography for computer science~\cite{dblp_ref,pham_2010}. The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research. We construct clusters of articles using either direct citation or co-citations and match these clusters to ASJC categories to place them in context. We also aligned clusters from direct citations to those from co-citations and discuss our findings. Overall, we note cross category clusters with different degrees of interaction with fields outside computer science.
\clearpage
\section{Materials and Methods}
\label{sec:methods}

\emph{Overview.} Our underlying assumption is that, notwithstanding incomplete coverage, records in DBLP are greatly enriched for computer science~\cite{dblp_ref,pham_2010}. Therefore, the contents of DBLP are an excellent sample of the computer science literature to analyze. The workflow described in the following paragraphs of Materials and Methods, consists at a high-level of (i) merging the DBLP and Scopus datasets using digital object identifiers(DOIs) (ii) extracting cited references for the articles common to DBLP and Scopus (iii) clustering by direct citation and by our modification of co-citation based clustering. The outcome was a dataset of 8,000,411 publications.

@@

\emph{Direct Citation.} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, and that has previously been applied to citation data~\cite{subelj_clustering_2016}. We used v1.2 in our experiments. The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus, which requires the number of clusters to be formed as an input parameter. In preliminary experiments, we varied the number of clusters to be formed between 10 and 50 clusters (data not shown).  At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one,
so that 20 clusters is a good choice with respect to the criteria specified in~\cite{subelj_clustering_2016}. Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}), analogous to Level 1 of Waltman and van Eck's mapping of nearly 10 million publications but focused on the DBLP bibliography rather than a broader Web of Science sample~\cite{waltman_new_2012}.

@@

\emph{Co-citation.} For an alternate view of these DBLP data, we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles \cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}. Co-citation, first described independently by Small and Marshakova in 1973 \cite{marshakova-shaikevich_co-citation_1973}, provides insight into the emergence of new ideas derived from the association of previously independent ones. Unlike clustering by direct citation, where every input publication is assigned to a cluster and every citation is weighted equally, the co-citation relationship between papers is weighted to represent the strength of the co-citation history. Because this produces a weighted graph, clustering methods that address weights are required. Clustering by co-citation also considers weak inter-cluster interactions that involve modifications to standard clustering approaches. \cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.

@@

We began by identifying highly cited articles in \emph{comp} and selected those in the 90th percentile (212,311 articles). We then identified ~4.3 million publications in Scopus that cite these 212,311 articles. For each of the 4.3 million citing publications in turn, 
all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication. The cited reference pairs generated were then restricted to those where both members of a pair were in the 
set of 212,311 highly cited papers previously identified. A total of 46,463,117 unique co-cited pairs were thus obtained. The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine 
formula~\cite{salton_citation_1979} to limit dominance by areas with high citation activity. These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.

@@

\clearpage
\section{Results}
\label{sec:results}

@@

To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other (Fig.~\ref{fig:graclus_cocit_fig}).
 At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters. This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and,  by extension, tend towards disciplinarity rather than interdisciplinarity.
\clearpage
\section{Discussion} 
Considering expansion and diversification of the field of computer science, we revisited its characterization by Salton and Bergmark in 1979~\cite{salton_citation_1979}. In comparison to \cite{salton_citation_1979}, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  approximately 7 million and 88 million publications respectively. By linking the two datasets, we were able to harvest citation data as well as other metadata that enabled theo construct article level clusters in two different ways and reconciliation with the Scopus ASJC classification, for a journal level perspective.

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
\includegraphics[scale=0.6]{graclus_comparison.pdf}
% generated by conductance.R script
% figure caption is below the figure
\caption{Conductance measurements of clusters generated by Graclus of the direct citation dataset.  2,685,356 DBLP publications, 7,129,006 cited references, and 44,296,381 citations were clustered using Graclus into 18 (grac\_18), 20 (grac\_20), or 22 (grac-22) clusters. Conductance, $\phi(S)$, was measured for these clusters considering only the edges between publications using the formula: $\phi(S)=|\partial(S)|/min(vol(S),2m-vol(S)$, where $\partial(S)$ is the boundary (number of edges leaving a set), vol(S) is volume of a set of vertices as the sum of the degrees of the vertices in a set, and $m$ is the number of undirected edges in a set~\cite{shun_parallel_2016}.}
\label{fig:graclus_comparison_conductance}       
\end{figure}

@@

\begin{table}[ht]
\caption{Descriptive statistics of the 20 clusters produced from the \emph{comp} dataset using Graclus (direct citation).  The number of publications in each cluster, the conductance~\cite{shun_parallel_2016} of each cluster, the total number ASJC minor subject area labels assigned to publications in each cluster and the number of 
unique labels in each cluster are shown.}
\label{tab:graclus}       
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
\noalign{\smallskip}\hline\noalign{\smallskip}
0 & 111,294 & 0.12 & 265,664 & 142 \\ 
1 & 117,057 & 0.14 & 246,960 & 166 \\ 
2 & 116,251 & 0.11 & 280,602 & 165 \\ 
3 & 353,366 & 0.15 & 881,693 & 200 \\ 
4 & 145,081 & 0.09 & 349,020 & 154 \\ 
5 & 92,097 & 0.17 & 248,168 & 186 \\ 
6 & 71,865 & 0.15 & 199,681 & 163 \\ 
7 & 179,927 & 0.18 & 465,181 & 202 \\ 
8 & 302,656 & 0.18 & 760,117 & 214 \\ 
9 & 69,520 & 0.19 & 197,031 & 174 \\ 
10 & 42,462 & 0.10 & 102,838 & 141 \\ 
11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
12 & 70,738 & 0.21 & 216,546 & 179 \\ 
13 & 105,232 & 0.17 & 289,318 & 187 \\ 
14 & 199,176 & 0.15 & 551,657 & 208 \\ 
15 & 64,384 & 0.17 & 195,679 & 167 \\ 
16 & 89,340 & 0.11 & 240,157 & 158 \\ 
17 & 50,817 & 0.14 & 181,531 & 179 \\ 
18 & 43,113 & 0.20 & 108,518 & 177 \\ 
19 & 12,615 & 0.80 & 36,583 & 229 \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{Nucleating co-citations. For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label.}
\label{tab:centroid}       
\begin{tabular}{p{8 mm}p{42 mm}ll}
\hline\noalign{\smallskip}
Cluster & Nucleating Pair & NCF & Label \\
\noalign{\smallskip}\hline
18670 & 10.1016/j.cam.2015.03.057 10.1016/j.sigpro.2015.10.009 & 0.92 & Dynamical Systems \\
18892 & 10.1287/msom.1080.0228 10.1287/msom.1060.0190 & 0.72 & Operations Research\\ 
18918 & 10.1007/s11128-010-0177-y 10.1007/s11128-013-0567-z & 0.83 & Image Processing\\ 
18947 & 10.1109/TASE.2011.2160452 10.1109/TASE.2011.2178023 & 0.77 & Robotics\\ 
18956 & 10.1109/ICCV.2017.32 10.1109/ICCV.2017.31 & 0.84 & Computer Vision\\ 
18972 & 10.1109/ASE.2013.6693094 10.1145/2568225.2568254 & 0.69 & Software \\ 
18974 & 10.1016/j.amc.2009.03.023 10.1016/j.amc.2010.07.064 & 0.54 & Applied Mathematics\\ 
18983 & 10.1137/110848864 10.1137/110848876 & 0.66 & Optimization\\ 
18997 & 10.1504/IJMIC.2014.065339 10.1504/IJMIC.2015.068871 & 0.91 & Chaotic Systems \\ 
19008 & 10.1016/j.chb.2008.12.013 10.1016/j.chb.2008.12.012 & 0.63 & Hum Comp Interaction\\ 
19009 & 10.1109/AVSS.2017.8078491 10.1109/ICCV.2017.206 & 0.78 & Artificial Intelligence\\ 
19013 & 10.1145/2508859.2516668 10.1007/978-3-642-42045-0\_15 & 0.88 & Security\\ 
19026 & 10.1145/2541940.2541942 10.1109/HPCA.2014.6835965 & 0.81 & Architecture\\ 
19027 & 10.1016/S0305-0548(03)00250-8 10.1016/j.ejor.2006.03.013 & 0.82 & Graph algorithms\\ 
19030 & 10.1109/ICDE.2008.4497474 10.14778/1687627.1687666 & 0.69 & Databases \\ 
19031 & 10.1109/TMM.2005.843347 10.1109/TCE.2005.1405724 & 0.55 & Networks\\ 
19033 & 10.1109/TIFS.2014.2327757 10.1109/TCYB.2014.2376934 & 0.78 & Facial Recognition\\ 
19034 & 10.1016/j.neuroimage.2013.05.018 10.1016/j.neuroimage.2014.06.016 & 0.63 & Neurology\\ 
19035 & 10.1002/int.21933 10.1002/int.21927 & 1.09 & Intelligent Systems\\ 
19036 & 10.1006/jsco.2000.0402 10.1006/jsco.2000.0403 & 0.73 & Comp Geometry\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{Nucleating co-citations. Manually assigned labels for nucleating co-cited pairs (Table~\ref{tab:centroid}) are matched to the ASJC minor subject area that constitutes the largest fraction (shown as percentage in parentheses) of all nodes in the cluster. In cases of ties, both minor subject areas are shown. Abbreviations: Electrical and Electronic Engineering (EEE); Control and Systems Engineering (CSE).}
\label{tab:centroid_reconcile}       
\begin{tabular}{p{8 mm}p{42 mm}l}
\hline\noalign{\smallskip}
Cluster & Label & Minor Subject Area \\
\noalign{\smallskip}\hline
18670 & Dynamical Systems & (i) EEE (14) (ii) CSE (14) \\
18892 & Operations Research & EEE (24) \\ 
18918 & Image Processing & (i) EEE (17) (ii) Software (17) \\ 
18947 & Robotics & Software (12) \\ 
18956 & Computer Vision & Computer Graphics and Computer-Aided Design (21)\\ 
18972 & Software & Software (55) \\ 
18974 & Applied Mathematics & Applied Mathematics (12)\\ 
18983 & Optimization & EEE (35) \\ 
18997 & Chaotic Systems & CSE (23)\\ 
19008 & Hum Comp Interaction & Education (19)\\ 
19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
19013 & Security & Computer Science(all) (29)\\ 
19026 & Architecture & EEE (35) \\ 
19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
19030 & Databases & Software (19)\\ 
19031 & Networks & EEE (32)\\ 
19033 & Facial Recognition & Computer Vision and Pattern Recognition (18)\\ 
19034 & Neurology & Neurology (12)\\ 
19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
19036 & Comp Geometry & Software (10)\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage
